---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: xelatex
    template: "cam-latex-syllabus.tex"
geometry: margin=1in

title: "POSC 2103--007: Introduction to United States Government"
author: Dr. Cameron Wimpy
date: "Spring 2020"

email: "cwimpy@astate.edu"
web: "cwimpy.com"
officehours: "MW: 10:00--11:30 a.m. | R: 9:30--11:30 a.m."
office: "HSS: 3022"
classroom: "HSS: 3005"
classhours: "MW 12:30--1:45 p.m."

fontsize: 11pt
header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2020-01-13")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," -- ",tfri)
 return(tmp)
}

library(RefManageR)
bib <- ReadBib("amgov.bib") 
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)
```

# Course Description

This course serves as an introduction to: **The constitution, government, and politics of the United States.** The main goal of this course is to help you understand the structure and processes of the American political system. This is accomplished by reading about and analyzing:


- the key structures and institutions of government;
- relevant political actors such as political parties, interest groups and the media;
- the electoral process;
- voters and voting behavior.

# General Education Goal

- **Developing a strong foundation in the social sciences**:  Students should be aware of the diverse systems developed by humans to manage and structure our relationships with one another.  Students should prepare for the full range of public and private roles they are expected to fulfill as citizens, decision-makers and human beings in a democratic America and in a global society.

# Student Learning Outcomes

1. Explain the processes and effects of individual and group behavior

2. Analyze events in terms of the concepts and relational propositions generated by the social science tradition

3. Have a working knowledge of the government of the United States

4. Understand the challenges of governing in the United States

5. Explain how individuals and groups interact to produce their collective experience

6. Analyze empirical evidence to make reasoned arguments about government of the United States

\clearpage

# Course Requirements

## Textbook

This textbook is required. You can search for it online, in the bookstore, and view the publisher's website via this ISBN: [978-0190299903](http://global.oup.com/ushe/product/american-government-9780190299903). The book includes a student companion website that has additional materials to help you study and further explore government in the United States.

\hangindent=0.7cm
```{r, echo = FALSE, results="asis"} 
bib["Krutz:2021"]
``` 

## Technology

You will need to use your A-State email and have access to Blackboard. If there is any issue with these items you should me know by the second day of class. 

## Exams

There will be three multiple choice exams. The exams will take place via Blackboard (make sure you can access Blackboard by the second day of class). Each exam will consist of 50 questions taken from the lectures and readings. The final exam is \underline{not} comprehensive.

## Current Events

Given the topic of this course we will begin each class with a brief (and sometimes not so brief) discussion of current events as they relate to government in the United States. Please be prepared to participate in this discussion by reading the news at your favorite source. If you do not have a favorite source, then I suggest looking at a range of outlets. I often read: _The New York Times_, _The Washington Post_, _The Economist_, _Fox News_, _CNN_, _BBC News_, _Real Clear Politics_, _Five Thirty Eight_, and _Politico_ among others. Please bring in any articles or topics you would like to discuss. There are also some great podcasts/radio options including: _NPR_, _FiveThirtyEight_, and _The Daily_ (NYT). Please refrain from looking up current events in real time during class. This is disruptive, rude, and signals a lack of preparation at best. Come prepared with topics and details---please do not just blurt out headlines.

# Course Policies

These course policies are subject to change, but assume they are in effect unless you hear otherwise from Dr. Wimpy.

## Academic Freedom

We are living in a particularly polarized period of American politics, and that means that some of us will often disagree with differing (but typically reasonable) points of view. Disagreement and debate is a healthy part of our political system so please be respectful of your classmates as they share their perspectives. Please know you have complete academic freedom to express your opinions and thoughts on U.S. Government. Having said that, any type of hateful or insulting discussion will not be tolerated. 

## Grading Policy

Your grade will consist of your performance on the exams along with your ability to participate in the class through attendance and discussions of course material/current events. The evaluation breakdown will be as follows:

```{r grade_weights_data, include=FALSE}
library(tidyverse)
library(knitr) 
library(kableExtra)

dt <- read_csv("weights.csv")
dt2 <- read_csv("scale.csv")

```

```{r grade_weights, echo=FALSE}
kable(dt, "latex", booktabs = T) %>% 
  kable_styling(latex_options = "striped")
```

The grading system will follow the [A-State convention](https://www.astate.edu/college/graduate-school/academic-policies/). Letter grades will be assigned as follows:


```{r grade_scale, echo=FALSE}
kable(dt2, "latex", booktabs = T) %>% 
  kable_styling(latex_options = "striped")
```

## E-mail Policy

I am usually quick to respond to student e-mails during regular business hours. However, student e-mails tend to do several things that try my patience. The following points outline why I will not respond to certain e-mails students send. _Note that some of these may not apply specifically to this course._

1. The student could answer the inquiry by reading the syllabus.
2. The student provides am unsolicited reason for missing class (other than exam days). I do not need to know the exact reason why you missed class. Students with excusable absences are responsible for giving me a note that documents the reason for a missed exam. Anything else is just extra information.
3. The student wants to know what topics were missed during a missed/skipped class. The answer is always "you missed what was on the syllabus."
4. The student is not professional in the e-mail. Please consider writing professional e-mails, it's a good habit that will pay off one day. That means you begin the e-mail with a greeting and that you end it with a closing. You can learn more from sites like this: [https://www.indeed.com/career-advice/career-development/how-to-write-a-professional-email](https://www.indeed.com/career-advice/career-development/how-to-write-a-professional-email)
5. The student wants to know something that is readily discernible from Blackboard (e.g., "how many discussion posts do I have left?," "what is my current grade?").
6. The student is requesting an extension on an assignment for which the syllabus already established the deadline. The answer is always "no."
7. The student is ["grade grubbing"](https://www.math.uh.edu/~tomforde/GradeGrubbing.html) or asking to round up a grade outside of the rounding outlined in the grading policy above. The answer is always "no."
8. The student is asking for an extra credit opportunity, a request that amounts to more grading for the professor. The answer is "no."

## Make-Up Exam Policy

There are no make-ups for missed exams unless there is a valid excuse. Don't bother asking.

## Extra Credit/Grade Change Policy

I do not give extra credit and grades will only be changed in the event of a calculation error. Do not bother asking about anything else.

## Attendance

Attendance is required and I will take roll each class. See the [student handbook](http://www.astate.edu/a/student-conduct/student-standards/handbook-home.dot) for the University policies on attendance. 

## Laptops, Phones, & Tablets

Laptops and tablets are allowed in the classroom insofar as they are used to take notes and/or accessing the online text (should you opt for the online edition). Phones are not allowed to be out during class time under any circumstances. If you have an emergency, please leave the class and take care of it. Otherwise it can wait. If I see abuse of the laptop/tablet policy I reserve the right to disallow these during class time unless there is a documented and approved exception. 

## Academic Dishonesty Policy

Plagiarism (the act of taking and/or using the ideas, work, and/or writings of another person as one’s own) is a serious offense against academic integrity which could result in failure for the paper or assignment, failure for the course, and/or expulsion from Arkansas State University.

Cheating is an act of dishonesty with the intention of obtaining and/or using information in a fraudulent manner. For further information, including specifics about what constitutes plagiarism or cheating, see ASU’s Academic Integrity Policy in the student [handbook](https://www.astate.edu/a/student-conduct/student-standards/handbook-home.dot).

## Disabilities Policy

Any student in this course who has a disability that may prevent him/her from fully participating in this course should contact Disability Services at (870) 972-3964 (or here: [https://www.astate.edu/disability](https://www.astate.edu/disability)) as soon as possible so we can make the necessary accommodations to facilitate your educational opportunity.

## Copyright & Fair Use Statement

The materials used in this course are subject to copyright laws. For those materials which neither I nor ASU owns the copyright, I have either obtained a license for use or am using the materials in a manner that I reasonably believe is in compliance with the Fair Use exception to the copyright laws. The other materials used in this course are copyrighted. By this, I mean all materials generated for this class, which include but are not limited to syllabi, exams, lectures, quizzes, assignments, and any other document I post in Blackboard. Because these items are copyrighted, you do not have the right to copy and distribute any course materials unless I, or the document publishers, expressly grant permission.

\newpage

# Tentative Class Schedule

Important: class readings are subject to change, contingent on mitigating circumstances and the progress we make as a class.  Students are encouraged to check the Blackboard announcements section and any e-mails from me for updates. 

## `r advdate(mon, 1)`: Course Introduction, Topic Introduction (U.S. Government)

### Read:

- The Course Syllabus

- Chapter 1
    
## `r advdate(mon, 2)`: The Constitution

### Read:

- Chapter 2

##  `r advdate(mon, 3)`: Federalism 

### Read:

- Chapter 3

##  `r advdate(mon, 4)`: Civil Liberties 

### Read:

- Chapter 4

##  `r advdate(mon, 5)`: Civil Rights

### Read:

- Chapter 5

##  `r advdate(mon, 6)`: Exam 1 

### Read:

- Chapters 1--5 (as needed to review)

### Activities:

- Exam 1 Review (M) | Please be prepared with questions!

- Exam 1 (W) | Covers Chapters 1--5

##  `r advdate(mon, 7)`: Public Opinion and Political Participation | Political Parties

### Read:

- Chapters 6--7

##  `r advdate(mon, 8)`: Campaigns and Elections

### Read:

- Chapter 8

##  `r advdate(mon, 9)`:  Interest Groups

### Read:

- Chapter 9

##  `r advdate(mon, 10)`: Media & Politics

### Read:

- Chapter 10

##  `r advdate(mon, 11)`: Spring Break | No Class!

##  `r advdate(mon, 12)`: Exam 2

### Read:

- Chapters 6--10 (as needed to review)

### Activities:

- Exam 2 Review (M) | Please be prepared with questions!

- Exam 2 (W) | Covers Chapters 6--10

##  `r advdate(mon, 13)`: Congress

### Read:

- Chapters 11

##  `r advdate(mon, 14)`: The Presidency

### Read:

- Chapter 12



##  `r advdate(mon, 15)`: Bureaucracy

### Read:

- Chapter 13

##  `r advdate(mon, 16)`: Courts, Judges, & The Law 

### Read:

- Chapter 14

### Activities:

- Exam 3 Review (W) | Please be prepared with questions!

##  `r advdate(mon, 17)`: Exam 3

### Read:

- Chapters 11--14 (as needed to review)

- Exam 3 (M) | Covers Chapters 11--14

### Activities:

- **The Final Exam is Monday, May \nth{4} @12:30 p.m.**
